Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-06-26 conclusion.tex
ongoing refinement. but more in conclusion.

More generally, this paper highlights the fundamental role of WMS for
experimental science. HEP was amongst the first, if not the very first
experimental community to realize the importance of using WMS to manage their
computational campaign(s). As computing becomes increasingly critical for a
range of experiments, the impact of WMS on HEP foreshadows the importance of
WMS for other experiments (such as SKA, LSST etc.). % and their computational
campaigns. These experiments will have their own workload characteristics,
resources types and federation constraints, as well metrics of performance.
The design and experience captured in this paper will prove invaluable for
designing WMS to support computational campaigns and will provide a baseline
to evaluate the relative merits of different approaches.

>>>>

% More generally, this paper highlights the fundamental role of WMS for
% experimental science.

HEP was amongst the first, if not the first experimental community to realize
the importance of using WMS to manage their computational campaign(s). As
computing becomes increasingly critical for a range of experiments, the
experience foreshadows the importance of WMS for other experiments (such as
SKA, LSST etc.).  These experiments will have their own workload
characteristics, resources types and federation constraints, as well metrics
of performance. The experience captured in this paper will prove
invaluable for designing WMS for computational campaigns and will provide a
baseline to evaluate the relative merits of different approaches.
